The Midplane is Not a Plane: Implications for {\em Gaia}

### 2019-03-25 paper/ms.tex
Add text for chervin midplane fig

>>>>

We compute the same midplane variation in Figure~\ref{fig:midplane_chervin},
but for the toy simulation of a Sagittarius encounter
\citep{2018MNRAS.481..286L}. Again we have subtracted a best fit curve of the
form $\text{A} \sin{\left(\phi + \text{B}\right)} + \text{C}$, with the values
for $\text{A}$, $\text{B}$, and $\text{C}$ being \Gus{something},
\Gus{something}, and \Gus{something else}, respectively. In the first two
panels, we see that the midplane is relatively flat in the inner galaxy. But
additional encounters drive strong midplane variation. In the third panel, we
see a strong $m=2$ mode develop, consistent with the $R=8\,\kpc$ panel of
Figure~17 in \citet{2018MNRAS.481..286L}.
